Galaxy Clustering Constraints on the Galaxy Size--Halo Connection

### 2017-08-31 paper/galsize_paper.tex
Corrected typo

The salient feature of the clustering ratio measurements is that they are negative: for either disk- or bulge-dominated samples, small galaxies cluster more strongly than large galaxies of the same stellar mass threshold, a new result. This feature also holds true for model galaxies, for which both $\rhalfbulge$ and $\rhalfdisk$ scale in power law proportion to $\rvir.$ Since halo mass $\mvir$ scales as $\rvir^{1/3},$ and clustering is a strong function of $\mvir,$ the result may seem surprising.

@@

In the {\tt UniverseMachine}, and in any quantitatively successful cosmological model of the galaxy formation, central galaxies are preferentially more star-forming relative to satellites of comparable stellar or halo mass. Since bluer galaxies are diskier than redder galaxies, our model centrals will be diskier than satellites. Our galaxy profile model has $\adisk=7\abulge,$ and so satellite galaxies will be smaller than centrals due to the $\bt-\ssfr$ correlation. These simultaneous features alone will naturally result in the negative sign of the clustering ratios seen in Figure~\ref{fig:clustering_ratio_upshot}.

>>>>

The salient feature of the clustering ratio measurements is that they are negative: for either disk- or bulge-dominated samples, small galaxies cluster more strongly than large galaxies of the same stellar mass threshold, a new result. This feature also holds true for model galaxies, for which both $\rhalfbulge$ and $\rhalfdisk$ scale in power law proportion to $\rvir.$ Since halo mass $\mvir\propto\rvir^{3},$ and clustering is a strong function of $\mvir,$ the result may seem surprising.

@@

In the {\tt UniverseMachine}, and in any quantitatively successful cosmological model of galaxy formation, central galaxies are preferentially more star-forming relative to satellites of comparable stellar or halo mass. Since bluer galaxies are diskier than redder galaxies, our model centrals will be diskier than satellites. Our galaxy profile model has $\adisk=7\abulge,$ and so satellite galaxies will be smaller than centrals due to the $\bt-\ssfr$ correlation. These simultaneous features alone will naturally result in the negative sign of the clustering ratios seen in Figure~\ref{fig:clustering_ratio_upshot}.
